Concretizing the Process Hitting into Biological Regulatory Networks

### 2013-04-18 parts/infer-param.tex
fix property of well-formed PH for parameter inference

\begin{property}[Well-formed PH for parameter inference]\label{pro:wf-ph-K}
A PH is well-formed for parameter inference if and only if
it is well-formed for IG inference, and
the IG $(\Gamma, E_+, E_-, E_\pm)$ inferred by \pref{pps:inference-IG}
verifies $E_\pm=\emptyset$ and if the following property holds:
\begin{align}
\begin{split}
\forall b\in \GRNreg{a} &,
	\forall (i,j\in\levels{b}{a} \vee i,j\in\ulevels{b}{a}), \\
& \qquad	\forall c, ( (b\neq a\wedge c=a) \vee (c\in\PHpredec{a} \wedge b\in\PHdirectpredec{c})), \\
& \qquad \qquad
			\PHfrappe{b_i}{c_k}{c_l}\in\PHa \Leftrightarrow
				\PHfrappe{b_j}{c_k}{c_l}\in\PHa
\end{split}
\label{eq:wf-levels}
\end{align}
\end{property}

>>>>

\begin{property}[Well-formed PH for parameter inference]\label{pro:wf-ph-K}
A PH is well-formed for parameter inference if and only if
it is well-formed for IG inference, and
the IG $(\Gamma, E)$ inferred by \pref{pps:inference-IG}
verifies the following property:
\begin{align}
\begin{split}
\forall b\in \GRNreg{a} &,
	\forall (i,j\in\levels{b}{a} \vee i,j\in\ulevels{b}{a}), \\
& \qquad \forall c \in \Gamma, ( (b\neq a\wedge c=a) \vee (c\in\PHpredec{a} \wedge b\in\PHdirectpredec{c})), \\
& \qquad \qquad
			\PHfrappe{b_i}{c_k}{c_l}\in\PHa \Leftrightarrow
				\PHfrappe{b_j}{c_k}{c_l}\in\PHa
\end{split}
\label{eq:wf-levels}
\end{align}
\end{property}
